---
title: "X-Journalism 2"
output:
  html_notebook: default
  html_document: 
    toc: yes
    number_sections: yes
---

* Filterung des Twitterkorpus auf Basis der Bi-Gramme
* Sentiment detection und die offensive language detection
* Maxqda Export für die weitere qualitative Analyse

```{r readdata, message=FALSE}
options(stringsAsFactors = F, scipen = 999)

library(dplyr)

# read data 
csv_files <- list.files("data3", pattern = "*.tsv", full.names = T)
twitterdata <- do.call(rbind, lapply(csv_files, read.csv, sep = "\t", header = F, encoding = "UTF-8"))
colnames(twitterdata) <- c(
  "id", 
  "created_at", 
  "text", 
  "in_reply_to_status_id", 
  "in_reply_to_user_id", 
  "in_reply_to_screen_name",
  "user.id",
  "user.name",
  "user.screen_name",
  "verified",
  "followers_count",
  "friends_count",
  "location",
  "urls"
)

# convert dates
old_locale <- Sys.getlocale("LC_TIME")
invisible(Sys.setlocale("LC_TIME", "C"))
format.str <- "%a %b %d %H:%M:%S %z %Y"
twitterdata <- twitterdata %>% 
  mutate(
    date = as.POSIXct(strptime(created_at, format.str, tz = "GMT"), tz = "GMT")
  ) %>%
  mutate(
    year = format(date, "%Y")
  )
invisible(Sys.setlocale("LC_TIME", old_locale))

# filter for urnalism
twitterdata <- twitterdata[grepl("urnalism", twitterdata$text, ignore.case = T), ]

# filter for retweets 
twitterdata <- twitterdata[!grepl("^RT ", twitterdata$text, perl = T), ]

# filter duplicates
twitterdata <- twitterdata[-which(duplicated(twitterdata$id)), ]

print(head(twitterdata))
```

# Filter corpus

```{r filtercorpus, message=F}
require(quanteda)

# filter for years
twitterdata <- twitterdata[twitterdata$year %in% c("2019", "2020"), ]

# filter for coded bigrams
coded_data <- read.csv("bigram_JB_LS_WL.csv", encoding = "UTF-8")
bigram_patterns <- phrase(coded_data$collocation)
bigram_patterns <- bigram_patterns[coded_data$xjournalism == 1]
bigrams_concatenated <- unlist(lapply(bigram_patterns, paste0, collapse = "_"))

# create tokens object
colnames(twitterdata)[1] <- "doc_id"
tw_tokens <- corpus(twitterdata) %>%
  tokens() %>%
  tokens_tolower(keep_acronyms = T)

# concatenate bigrams
tw_tokens <- tokens_compound(tw_tokens, bigram_patterns)

# count bigrams
tw_dfm <- dfm(tw_tokens, tolower = F)
tw_dfm <- tw_dfm[, bigrams_concatenated]
tw_dfm <- tw_dfm > 0 # binary counts only
tw_dfm <- tw_dfm[rowSums(tw_dfm) > 0, ]

# add bigram label to each tweet
df <- reshape2::melt(as.matrix(tw_dfm))
df <- df[df$value == T, c("docs", "features")]
colnames(df) <- c("doc_id", "xjournalism")
twitterdata <- twitterdata %>%
  left_join(df)

# remove tweets without bigram label
twitterdata <- twitterdata[!is.na(twitterdata$xjournalism), ]
```

How many did we get?

```{r variations, message=F}
twitterdata %>%
  group_by(xjournalism) %>%
  count()
```


# Sentiment Analysis 

We use the NTLK Vader SentimentIntensityAnalyzer for sentiment scoring (a dictionary based method).

```{r sentiment}
# export tweets to csv
write.csv(twitterdata[, c("doc_id", "text")], file = "all_tweets.csv", fileEncoding = "UTF-8")
# run python script for sentiment and offensive language detection

# load results from python script
all_scores <- read.csv("all_tweets_scored.csv", encoding = "UTF-8")
twitterdata$sentiment_score <- all_scores$score
twitterdata$sentiment <- "POSITIVE"
twitterdata$sentiment[twitterdata$sentiment_score == 0] <- "NEUTRAL"
twitterdata$sentiment[twitterdata$sentiment_score < 0] <- "NEGATIVE"

# how many of each label?
print(table(twitterdata$sentiment))

# how positive is the usage context if a xjournalism term
twitterdata %>%
  group_by(xjournalism) %>%
  dplyr::summarize(Mean = mean(sentiment_score)) %>%
  arrange(desc(Mean))
```

# Offensive Language Detection

We use the approach as published in:

```
Wiedemann, G., Yimam, S. M., & Biemann, C. (2020, December). UHH-LT at SemEval-2020 task 12: Fine-tuning of pre-trained transformer networks for offensive language detection. In Proceedings of the Fourteenth Workshop on Semantic Evaluation (pp. 1638-1644).
```

Run "oe20_classification.ipynb" on `all_tweets.csv` and load results. Take care that Twitter usernames and URLs are replaced according to the model.

```{r old_labels, message=F}
# read binary labels from machine classifier
all_labels <- readLines("all_tweets_labeled.csv", encoding = "UTF-8")
twitterdata$offensive <- all_labels
twitterdata$offensive_score <- ifelse(all_labels == "OFF", 1, 0)

# how offensive is the usage context if a xjournalism term
twitterdata %>%
  group_by(xjournalism) %>%
  dplyr::summarize(Mean = mean(offensive_score)) %>%
  arrange(desc(Mean))
```


# REFI-QDA Export 

Unfortunately, we have to get rid off emojies to be able to correctly export tweets to MaxQDA. Not sure if this is an error of R or MaxQDA ...

```{r refi}
# csv first
write.csv(twitterdata, file = "xjournalism_twitter.csv", fileEncoding = "UTF-8")

twitterdata <- twitterdata %>%
  arrange(xjournalism)

# now export via refi-qda standard (this takes several minutes)
source("dataframe_to_refi.R")
dataframe_to_refi_group_by(
  twitterdata, 
  c("xjournalism", "sentiment", "offensive", "doc_id"), # "user.screen_name", "verified" 
  "xjournalism.qdpx",
  group_var = "xjournalism"
)
```
